% !TeX program = xelatex
% !TeX encoding = UTF-8

\documentclass[xcolor=table,dvipsnames,svgnames,aspectratio=169]{beamer}

\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{array}
\usepackage{tabularx}
\usepackage{colortbl}

\graphicspath{{figures/}}

\usetheme[max,blue]{sjtubeamer}

\title[FluxLink · Project Proposal]%
  {\textbf{FluxLink}: A Unified Adaptive Platform\\for Secure Multi-Transport File Transfer}
\subtitle{VE441 · App Development for Entrepreneurs · Project Proposal}
\author{Sun Qizhen \and Zhang Jinbin \and Li Yuhao \and He Yumeng}
\institute[UM-SJTU JI]{UM-SJTU Joint Institute · Shanghai Jiao Tong University}
\date{2025}

\begin{document}

\maketitle

% ----------------------------------------------------------------
% Elevator Pitch
% ----------------------------------------------------------------
\begin{frame}{FluxLink --- Elevator Pitch}
  \begin{block}{}
    \centering\large\itshape
    Never waste time choosing how to send a file again ---\\
    FluxLink automatically selects the fastest, most secure transfer path\\
    across any platform and any network.
  \end{block}

  \vspace{1.5em}

  \begin{columns}[c]
    \column{0.5\textwidth}
    \begin{itemize}
      \item \textbf{Zero decision cost} --- routing is automatic
      \item \textbf{Any network} --- LAN, P2P, relay fallback
      \item \textbf{Any platform} --- Android, iOS, Desktop
    \end{itemize}
    \column{0.5\textwidth}
    \begin{itemize}
      \item \textbf{Uniform E2EE} --- all modes, all files
      \item \textbf{Encrypted chat} --- context stays private
      \item \textbf{No account required} --- pair via QR/token
    \end{itemize}
  \end{columns}
\end{frame}

% ----------------------------------------------------------------
% Table of Contents
% ----------------------------------------------------------------
\begin{frame}{Outline}
  \tableofcontents[hideallsubsections]
\end{frame}

\AtBeginSection[]{
  \begin{frame}
    \tableofcontents[currentsection,subsectionstyle=show/show/hide]
  \end{frame}
}

% ================================================================
\section{Team Members}
% ================================================================

\begin{frame}{Team Members}
  \textbf{Team Name:} NUUB \hfill \textbf{PM:} Zhang Jinbin

  \vspace{0.8em}

  \resizebox{\textwidth}{!}{%
    \begin{tabular}{llll}
      \toprule
      \textbf{Full Name} & \textbf{jAccount} & \textbf{Task Assignment} & \textbf{Technical Strengths} \\
      \midrule
      Sun Qizhen   & qz\_sun      & Product architecture · Protocol routing engine · Network path scoring & Networking · Distributed systems · System design \\
      Zhang Jinbin & moranxuege   & PM · Mobile client (Android/iOS) · Cross-platform UI/UX            & Android (Kotlin) · iOS (Swift) · UX implementation \\
      Li Yuhao     & y4954he      & End-to-end encryption · QR/token handshake · Encrypted chat         & Cryptography · Backend security · Protocol design \\
      He Yumeng    & 17521218310  & Relay server · Deployment · Testing · Cache policy                  & Backend · DevOps · QA · Django REST \\
      \bottomrule
    \end{tabular}%
  }

  \vspace{0.8em}

  \begin{columns}[t]
    \column{0.25\textwidth}
    \textbf{Product \& Research}\\[0.3em]
    \small Sun Qizhen\\routing logic \& protocol priority
    \column{0.25\textwidth}
    \textbf{Client \& UX (PM)}\\[0.3em]
    \small Zhang Jinbin\\mobile UI \& cross-platform
    \column{0.25\textwidth}
    \textbf{Networking \& Security}\\[0.3em]
    \small Li Yuhao\\E2EE model \& handshake
    \column{0.25\textwidth}
    \textbf{Backend \& QA}\\[0.3em]
    \small He Yumeng\\relay infra \& test coverage
  \end{columns}
\end{frame}

% ================================================================
\section{User Interview Questionnaire}
% ================================================================

\begin{frame}[shrink=8]{Interview Design --- Participants \& Venue}
  \begin{columns}[t]
    \column{0.5\textwidth}
    \begin{block}{How We Find Interviewees}
      \begin{itemize}
        \item SJTU engineering/CS communities
        \item GitHub discussions, V2EX, WeChat tech groups
        \item Screening: regularly transfer files across multiple devices/OS, and have encountered at least one of: size limits, incompatibility, network failure, privacy concerns
        \item \textbf{Avoid friends/family} --- reduce social desirability bias
      \end{itemize}
    \end{block}
    \column{0.5\textwidth}
    \begin{block}{Venue \& Session Structure}
      \begin{itemize}
        \item Remote via Tencent Meeting / Zoom
        \item 10--20 min per session
        \item One interviewer + one note-taker
        \item Recorded with consent
      \end{itemize}
      \vspace{0.5em}
      \begin{tabular}{ll}
        0--5 min  & Warm-up, device context \\
        5--15 min & Pain stories, failure scenarios \\
        15--20 min & Ideal workflow, retention \\
      \end{tabular}
    \end{block}
  \end{columns}
\end{frame}

\begin{frame}{Theme 1: Device Context \& Current Behavior}
  \textit{Goal: Establish devices/platforms used and current tools, without leading toward any product concept.}

  \vspace{0.8em}

  \begin{enumerate}
    \item[\textbf{Q1}] Walk me through the devices you use daily and how often they need to share files with each other.
    \item[\textbf{Q2}] Think back to the last few weeks --- what triggered your need to send a file, and to whom?
    \item[\textbf{Q3}] What apps or methods do you normally reach for? How did you settle on those tools?
    \item[\textbf{Q4}] When you're about to send a file, what goes through your head before deciding which tool to use?
  \end{enumerate}
\end{frame}

\begin{frame}{Theme 2: Pain Points \& Failure Stories}
  \textit{Goal: Surface real breakdown moments, workarounds, and emotional friction.}

  \vspace{0.8em}

  \begin{enumerate}
    \item[\textbf{Q5}] Walk me through the last time you sent a large file --- from the moment you decided to send it to delivery.
    \item[\textbf{Q6}] Has your usual method ever just stopped working? What happened, and what did you do instead?
    \item[\textbf{Q7}] When transferring between iPhone and Android, or phone and a different-OS computer, how do you handle that?
    \item[\textbf{Q8}] Describe a time when security/privacy crossed your mind during a file transfer. Did it change your behavior?
    \item[\textbf{Q9}] What does it feel like when a transfer fails or arrives corrupted? Tell me about a specific moment.
  \end{enumerate}
\end{frame}

\begin{frame}{Theme 3: Motivations, Ideals \& Accepted Friction}
  \textit{Goal: Understand retention drivers, unarticulated needs, and normalized workarounds.}

  \vspace{0.8em}

  \begin{enumerate}
    \item[\textbf{Q10}] When a file transfer tool works really well, what makes you keep coming back to it?
    \item[\textbf{Q11}] Describe your ideal file-sending experience for a scenario that comes up regularly for you.
    \item[\textbf{Q12}] What frustrations have you accepted as ``the way file transfer works'' --- things you've stopped trying to fix?
  \end{enumerate}
\end{frame}

% ================================================================
\section{Competitor Analysis}
% ================================================================

\begin{frame}{Market Overview}
  \begin{block}{The Fundamental Gap}
    Existing systems typically optimize for \textbf{exactly one transport pathway}. No single consumer app combines all approaches into a unified, adaptive experience.
  \end{block}

  \vspace{0.5em}

  \begin{columns}[c]
    \column{0.2\textwidth}
    \centering\small\textbf{Cloud Storage}\\[0.3em]
    \footnotesize Google Drive\\iCloud · Dropbox
    \column{0.2\textwidth}
    \centering\small\textbf{Messaging Apps}\\[0.3em]
    \footnotesize WeChat\\WhatsApp · Telegram
    \column{0.2\textwidth}
    \centering\small\textbf{Ecosystem / LAN}\\[0.3em]
    \footnotesize AirDrop\\Nearby Share
    \column{0.2\textwidth}
    \centering\small\textbf{Internet P2P}\\[0.3em]
    \footnotesize Send Anywhere\\Snapdrop
    \column{0.2\textwidth}
    \centering\small\textbf{PAKE Transfer}\\[0.3em]
    \footnotesize Magic Wormhole\\croc
  \end{columns}

  \vspace{0.8em}
  \centering\textbf{Competitors analyzed:} Google Drive · WeChat · AirDrop · Send Anywhere · Magic Wormhole
\end{frame}

\begin{frame}[shrink=12]{Competitor Profiles (1/2)}
  \begin{columns}[t]
    \column{0.5\textwidth}
    \begin{block}{Google Drive --- Cloud Storage}
      \small\begin{itemize}
        \item[\faPlus] Persistent storage; cross-device sync; 15 GB free; no recipient install
        \item[\faMinus] Double bandwidth (sender $\to$ server $\to$ receiver)
        \item[\faMinus] Metadata leakage; subscription pressure; unsuited for transient transfer
      \end{itemize}
    \end{block}
    \vspace{0.3em}
    \begin{block}{WeChat --- Messaging App}
      \small\begin{itemize}
        \item[\faPlus] 1.3B+ users; already in daily use; integrated cloud storage
        \item[\faMinus] 100 MB limit; aggressive compression; server upload bottleneck
        \item[\faMinus] Ecosystem lock-in; super-app surveillance risks
      \end{itemize}
    \end{block}
    \column{0.5\textwidth}
    \begin{block}{AirDrop --- Ecosystem LAN Transfer}
      \small\begin{itemize}
        \item[\faPlus] Fast (Bluetooth + Wi-Fi Direct); no account; no internet required
        \item[\faPlus] Seamless Apple-to-Apple UX
        \item[\faMinus] Apple-only; proximity-only; no fallback for remote scenarios
        \item[\faMinus] Contact-discovery leaks phone numbers and email addresses to passive attackers \textit{(Heinrich et al., 2021)}
      \end{itemize}
    \end{block}
  \end{columns}
\end{frame}

\begin{frame}[shrink=12]{Competitor Profiles (2/2)}
  \begin{columns}[t]
    \column{0.5\textwidth}
    \begin{block}{Send Anywhere --- Internet P2P}
      \begin{itemize}
        \item[\faPlus] Cross-platform (Android, iOS, Web); 6-digit key; no account; 4.3\faAndroid
        \item[\faMinus] No intelligent routing between LAN/P2P/relay; relay-dependent in most real-world conditions; no resume on failure; no encrypted chat alongside transfer
      \end{itemize}
    \end{block}
    \column{0.5\textwidth}
    \begin{block}{Magic Wormhole --- PAKE Transfer}
      \begin{itemize}
        \item[\faPlus] Strongest cryptographic model (SPAKE2); relay holds no plaintext; resists offline attack; open-source --- \textit{architecturally closest to FluxLink}
        \item[\faMinus] CLI-only; no mobile app; no LAN fast path (all traffic routed through relay even on same Wi-Fi); no resume; single centralized relay
      \end{itemize}
    \end{block}
  \end{columns}
\end{frame}

\begin{frame}{Comparison Table}
  \centering
  \resizebox{\textwidth}{!}{%
    \begin{tabular}{lcccccc}
      \toprule
      \textbf{Feature} & \textbf{Google Drive} & \textbf{WeChat} & \textbf{AirDrop} & \textbf{Send Anywhere} & \textbf{Magic Wormhole} & \textbf{FluxLink} \\
      \midrule
      Cross-platform          & \checkmark & Partial    & $\times$   & \checkmark & \checkmark & \textbf{\checkmark} \\
      LAN / local transfer    & $\times$   & $\times$   & \checkmark & $\times$   & $\times$   & \textbf{\checkmark} \\
      Internet / relay        & \checkmark & \checkmark & $\times$   & \checkmark & \checkmark & \textbf{\checkmark} \\
      \rowcolor{cprimary!15}
      Auto-routing            & $\times$   & $\times$   & $\times$   & $\times$   & $\times$   & \textbf{\checkmark} \\
      \rowcolor{cprimary!15}
      E2EE (all modes)        & $\times$   & $\times$   & Partial    & Partial    & \checkmark & \textbf{\checkmark} \\
      \rowcolor{cprimary!15}
      Encrypted chat          & $\times$   & $\times$   & $\times$   & $\times$   & $\times$   & \textbf{\checkmark} \\
      No account required     & \checkmark & $\times$   & \checkmark & \checkmark & \checkmark & \textbf{\checkmark} \\
      No ecosystem lock-in    & \checkmark & $\times$   & $\times$   & \checkmark & \checkmark & \textbf{\checkmark} \\
      Mobile app              & \checkmark & \checkmark & \checkmark & \checkmark & $\times$   & \textbf{\checkmark} \\
      Resume on failure       & $\times$   & $\times$   & $\times$   & $\times$   & $\times$   & \textbf{\checkmark} \\
      \bottomrule
    \end{tabular}%
  }
\end{frame}

% ================================================================
\section{Technical Differentiation}
% ================================================================

\begin{frame}[shrink=22]{Intelligent Transfer Routing Engine}
  \begin{block}{Core Insight}
    Every competitor optimizes a \textbf{single transfer modality} and asks users to manage the rest manually.\\
    FluxLink treats the protocol stack as a \textbf{scored decision}, not a user configuration.
  \end{block}

  \vspace{0.5em}

  \textbf{Priority chain (probed automatically after pairing):}

  \vspace{0.3em}

  \begin{enumerate}
    \item \textbf{mDNS-based LAN} --- lowest latency, highest throughput, no internet dependency
    \item \textbf{IPv6 direct P2P} --- increasingly viable on campus and carrier networks
    \item \textbf{QUIC/UDP hole-punching} --- rendezvous-assisted NAT traversal; no file content on relay
    \item \textbf{Centralized relay fallback} --- guarantees delivery under any condition; relay handles ciphertext only
  \end{enumerate}

  \vspace{0.5em}
  \textit{The user sees one consistent interaction: \textbf{pair, send, done}. Path degradation triggers silent fallback.}
\end{frame}

\begin{frame}[shrink=33]{Security Model \& Encrypted Chat}
  \begin{columns}[t]
    \column{0.5\textwidth}
    \begin{block}{Uniform Security Across All Modes}
      \begin{itemize}
        \item QR / short-code handshake establishes a session key (SPAKE2)
        \item All file chunks and chat messages encrypted \textbf{before leaving the device}
        \item Relay server never sees plaintext
        \item Relay-cached messages cleared weekly
      \end{itemize}
    \end{block}
    \column{0.5\textwidth}
    \begin{block}{Encrypted Chat Layer}
      \begin{itemize}
        \item \textbf{No competitor} integrates encrypted chat alongside file transfer
        \item The conversation about a file is as private as the file itself
        \item Same E2EE session --- no context leakage
      \end{itemize}
    \end{block}
  \end{columns}

  \vspace{1em}

  \begin{alertblock}{Why This is Hard to Copy}
    The routing engine cannot be added incrementally to a single-modality app. Competitors would need to simultaneously rebuild their network layer, session model, and security architecture --- at odds with their current business models and architectural philosophy.
  \end{alertblock}
\end{frame}

% ================================================================
% Closing
% ================================================================
\begin{frame}{Summary}
  \begin{columns}[c]
    \column{0.5\textwidth}
    \begin{block}{What We Bring}
      \begin{itemize}
        \item Intelligent multi-protocol routing engine
        \item Uniform E2EE across LAN, P2P, and relay
        \item Integrated encrypted chat
        \item No account, no ads, no decision cost
      \end{itemize}
    \end{block}
    \column{0.5\textwidth}
    \begin{block}{Next Steps}
      \begin{itemize}
        \item Conduct user interviews (10--15 participants)
        \item Synthesize pain points \& refine problem framing
        \item Prototype routing engine core
        \item Validate pairing UX with paper prototypes
      \end{itemize}
    \end{block}
  \end{columns}

  \vspace{1.5em}

  \centering\Large\textbf{Thank you --- Questions?}
\end{frame}

\makebottom

\end{document}
